---
title: "A tutorial for creating a R package and publish to GitHub"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Documentation

## Installing the 'mypackage' package
Install the development version using **devtools** package:
```{r, eval = FALSE}
devtools::install_github("jitonglou/mypackage")
```

## Quick usage overview

Load the package:
```{r, message = FALSE, warning = FALSE}
library(mypackage)
```

### Call functions in the package
```{r myfuncs}
add_one(1.5)
add_one_cpp(1.5)
```

### Benchmark functions
There are at least five functions/packages for measuring the running time of R code (`Sys.time` and `system.time`) or benchmarking R code (`rbenchmark`, `microbenchmark`, and `tictoc`). In this document, I take `microbenchmark` as an example, and additional examples can be found in [this blog](https://www.alexejgossmann.com/benchmarking_r/)
```{r benchmark}
library(microbenchmark)

check_for_equal_results <- function(values) {
  tol <- 1e-8
  max_error <- abs(values[[1]]-values[[2]])
  max_error < tol
}

mbm <- microbenchmark(
  "r" = {y = add_one(1)},
  "cpp" = {y = add_one_cpp(1)},
   check = check_for_equal_results
)

mbm
```
I used the function argument `check` to check for equality (up to a maximal error of `1e-8`) of the results returned by the two functions. If the results weren't equal, `microbenchmark` would return an error message.</br>
A great feature of `microbenchmark` is the integration with `ggplot2` for plotting benchmark results.
```{r visualize mbm, message = FALSE}
library(ggplot2)
autoplot(mbm)
```

In this case, the function coded in C++ is slower than the default addition operation in R.